\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{parskip}

\usepackage{xeCJK} 
\setCJKmainfont{Noto Sans CJK TC}

\usepackage{geometry}
\geometry{
 a4paper,
% total={210mm,297mm},
 left=1in,
 right=1in,
 top=1in,
 bottom=1in
}

\usepackage{fancyhdr}
\chead{\raisebox{0.7mm}{Test Problemset}}
\pagestyle{fancy}

\usepackage{csquotes}

\begin{document}

\pagenumbering{gobble}
\begin{center}
    {\LARGE Problem C}\\
    {\Large Circle or Square}\\
    {Time limit: 1 second}\\
    {Memory limit: 512 megabytes}
\end{center}

\textbf{\large Problem Description}

MZ has drawn a shape on a 2D-plane. It can be either a circle or a square. 
He will tell you a number $A$ and two points $(x_1,y_1)$ and $(x_2,y_2)$ 
which are on the boundary of the shape. He guarantees that the shape has the 
following two properties.
\begin{enumerate}
	\item The difference between $A$ and the area of the shape is at 
		most $10^{-5}$.
	\item The distance between $(x_1,y_1)$ and $(x_2,y_2)$ is maximized.
		Any two points on the boundary of the shape has distance at
		most $\sqrt{|x_1-x_2|^2+|y_1-y_2|^2}$.
\end{enumerate}
Please write a program to determine what the shape is.
In addition, you are also asked to compute the perimeter of the shape.

\textbf{\large Input Format}

The input is terminated by end-of-file, and there are at most 30 test cases.
Each test case is a line containing five numbers $A,x_1,y_1,x_2,y_2$
separated by blanks. $A$ is a positive real number. $x_1,y_1,x_2,y_2$ are 
integers in $[-100,100]$.

\textbf{\large Output Format}

For each test case, your program should output one line as the following.
\begin{itemize}
\item If the shape is a circle, then output ``\verb+Circle +$p$'' where $p$
	is the perimeter of the circle. 
\item If the shape is a square, then output ``\verb+Square +$p$'' where $p$ 
	is the perimeter of the square. 
\item Otherwise, output ``\verb+MZ is a liar!+'' to blame the problem 
	setter.
\end{itemize}
You answer will be considered as incorrect if some number has both absolute 
error and relative error greater than $0.0000005$.

\textbf{\large Sample Input}

\begin{verbatim}
1 1 0 0 1
3.1415926 0 0 0 2
2.5 0 0 0 2
\end{verbatim}

\textbf{\large Sample Output}
\begin{verbatim}
Square 4
Circle 6.28318530718
MZ is a liar!
\end{verbatim}

\end{document}
